Verification and Synthesis of Embedded Systems: \\ Advances and Challenges

### 2017-01-01 paper.tex
added new figures

Counter-Example Guided Inductive Synthesis (CEGIS) is currently the most popular approach to program synthesis in practice~\cite{David15}. CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement. These two connections, however, involve two specific steps: synthesizing a repair in the former case, and synthesizing an abstraction function in the latter.

@@

%32
\bibitem{Alur13}
Alur R., Bodík R., Juniwal G., Martin M., Raghothaman M., Seshia S., Singh R., Solar-Lezama A., Torlak E., Udupa A.:
\newblock {\em Syntax-guided synthesis}. 
\newblock In: Formal Methods in Computer-Aided Design, pp. 1--8, 2013.

>>>>

Counter-Example Guided Inductive Synthesis (CEGIS) is currently one of the the most popular approaches to program synthesis in practice~\cite{David15}. Figures~\ref{Counter-Example-Guided-Inductive-Synthesis} shows the CEGIS approach, which has close connections to algorithmic debugging using counterexamples and abstraction refinement. These connections involve two specific steps: synthesizing a repair in the former case, and synthesizing an abstraction function in the latter.
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.12]{figure4.eps}
	\caption{Counter-Example Guided Inductive Synthesis.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

@@

%32
\bibitem{Alur13}
Alur R., Bod\'{\i}k R., Juniwal G., Martin M., Raghothaman M., Seshia S., Singh R., Solar-Lezama A., Torlak E., Udupa A.:
\newblock {\em Syntax-guided synthesis}. 
\newblock In: Formal Methods in Computer-Aided Design, pp. 1--8, 2013.
